SPP-Perc: Peceptron Learning Based Enhanced Signature Path Prefetcher

### 2018-11-16 back.tex
Incorporating suggestions

\section{Background Work and Motivation}

@@

\subsection{Related Work}

The idea of prefetching has been around since Instruction Stream
Buffers were proposed by Jouppi.  \cite{ISB} Some of the earliest data
prefetchers developed to try to identify memory access patterns with a
constant stride pattern.  \cite{Smith,Baer,Stride} Major research was
dedicated to stride distance and depth prediction.
\cite{Decoupled,Adaptive} Newer prefetchers aimed at correlating
predictions with the past memory access addresses.
\cite{Address_Correlated,AMPM}

With time newer and more intricate prefetchers were
introduced~\cite{Wenisch_Temporal_Streaming,Stealth,Feedback_Directed,Coordinated,Bandwidth_Efficient,Pacman,TLB,Linearizing,Sandbox,VLDP,DoL,Domino}.
A whole class of streaming prefetchers developed on the lines of
Spatial / Temporal Memory
Streaming~\cite{Spatial_Pattern,SMS,Temporal_Instruction_Fetch,Off_Chip,STMS,SMS_JILP}.

Most modern prefetchers aim at identifying complex memory access
patterns in a given application.  This allows them to capture some of
the irregular patterns seen in pointer chasing data-structures.
Offset based prefetchers are a generalization of the next-line
prefetcher.  Some of the prominent prefetchers exploiting this idea
are Sandbox Prefetcher \cite{Sandbox} and the Best Offset Prefetcher
\cite{BOP} Another class of prefetchers is lookahead Prefetchers.
Such prefetchers try to speculate deep into the application's memory
access trail.  These include Path Confidence based Lookahead
Prefetching \cite{SPP} and Kill the Program Counter \cite{KPC}.

@@

\textit{Machine Learning and Prefetching:} Peled \textit{et.al.}
introduce interesting ideas for on-line Reinforcement Learning and
dynamically scaling the magnitude of feedback given to the baseline
prefetcher.  \cite{Semantics} The biggest challenge here is that it
relies on compiler support for getting features to build the context.

The paper by Liao \textit{et. al.} focuses on prefetching for data
center applications.  \cite{Datacenter} They use offline Machine
Learning Algorithms like SVMs and Logistic Regressions to do
parametric search for an optimal prefetcher configuration.

%% NOTE: The below paper is literally the same idea as ours. But poor implementation and no good results. How much to bash this paper?
Finally, the paper on Data Cache Prefetching with Perceptron
Learning~\cite{BadPerc} talks about the idea of two step prefetching.
The first step is an existing baseline prefetcher while the second
step is a perceptron based throttler.  The paper has lots of
limitations in terms of design and implementation.  That reflects in
the fact that it did not lead to any significant performance gain over
even the basic prefetchers like the Stride Prefetcher\cite{Stride} and
the Markov Prefetcher\cite{Markov}.

\subsection{Perceptron Learning in Architecture}

Perceptron learning for computer architecture design has been around
for a while.  It was first popularized by Jimenez \textit{et. al.} for
doing branch prediction. \cite{Perc_Branch} In it's original
implementation, the Program Counter of the instruction looking for a
branch prediction would index into a given table of perceptron
weights.  The retrieved weights would then be multiplied with the
history of branch outcomes stored in the History Register (which is a
feature) in a dot product fashion.  The sum obtained is thresholded at
0 \textit{i.e.}, if the prediction y\textsubscript{out} >= 0, the
prediction is made as \textit{true}, or branch taken.  Else if the sum
is < 0, the prediction is made as \textit{false}.

The structure that we use is derived from the model introduced in
Piecewise Linear Branch Prediction\cite{Piece_Linear}.  Here the
feature itself is used to index into a hash of perceptron weights.
This form of indexing makes sure that the hyper-plane learned by the
perceptron weights is able to differentiate between linearly
inseparable outcomes.  \textit{<Is it true? Not sure>}

Perceptron Learning for Reuse Prediction\cite{Perc_Reuse} extended the
hash perceptron architecture to perform prediction in context of cache
replacement.  Perceptron layer can learn to correlate the cache
replacement behaviour with a variety of features.  Each feature has
its dedicated table of perceptron weights which it indexes into.
Hence number of tables equals the number of features.  Once the
perceptron weights from all the tables are obtained, they're summed
and thresholded based on a pre-decided value.  This led to a
prediction mechanism that is highly accurate, has quick learning rate
and is adaptable to changing program behaviour.  The features
introduced in that paper were derived from Program Counters of the
current and the last few instructions and the memory address of the
current access.  Even with such basic features, high level of
correlation could be established by perceptrons.

The work was further extended by Multiperspective Reuse
Prediction\cite{Multiperspective}, which introduced a varied set of
parametric features.  Although design space exploration for feature
and parameter selection was a non-trivial task, once fixed, it could
give a cache replacement predictor highly suitable for the given set
of applications.

@@

\textit{Perceptron Update Rule:} In all the above implementations, a
uniform perceptron update principle is being followed.  The weights
need to be updated if the prediction was wrong or the predicted sum
does not cross a certain threshold.  After a certain training period,
these weights are proportional to the probability of the outcome being
true.  This training threshold makes sure that the perceptrons are
trained till a certain level of confidence and yet they are not
over-trained to the given set.  Care is taken that the weights
saturate at certain positive and negative values so that they remain
confined to the bit-width.  The same rules will be applied in the
discussion done in section XX on SPP-Perc learning algorithm.

\subsection{Prefetching with SPEC 2017}
\textit{<Discuss SPEC 2017 traces here>
<What are the possible graphs / analysis tools we can use for SPEC traces?>}

\subsection{Signature Path Prefetcher Architecture}
Since the work we have done builds heavily on SPP\cite{SPP}, we are
presenting a brief recap of the ideas introduced in the original
paper, especially with an eye towards their relevance in our work.
Signature Path Prefetcher (SPP) is a lookahead prefetcher and consists
of following structural components:

\textbf{Signature Table:} ST keeps track of 256 most recently accessed
pages.  It is meant to capture memory access patterns within a page
boundary.  SPP indexes into an entry of ST using the page number.  For
each entry corresponding to a page, ST stores the `last block offset'
and `old signature'.  Last block offset is the block offset of the
last memory access of that given page.  The block offset is calculated
with respect to the page boundary.  The signature is a 12-bit
compressed representation of the past few memory accesses for that
page.  The signature is calculated as:
$$New Signature = (\,Old Signature << 3 bits\,) \;\;XOR\;\; (\,Delta\,)$$ 
In case a matching page entry is found, the stored signature in the corresponding entry is retrieved.

Consider the case that incoming page number 10 with a block offset 3
finds a match in the ST.  The retrieved pattern signature is 0x30 and
the Last Offset is 1.  Since now there is the Last Block Offset (1),
Incoming Block Offset (3), Old Signature (0x30), and New Signature
calculated as per above equation (0x182), SPP can infer
non-speculatively that the given pattern of memory accesses (as
captured in the Old Signature) leads to the particular Delta.  In
general, Delta is defined as the difference between the prefetch
suggestion block and the initial block which triggered the prefetch.
In this case, since SPP is in learning phase, it is defined as the
difference between the Incoming Block Offset and the Last Block Offset
(+2 in this case).  This, in turn generates the new memory pattern
(New Signature).  This newly learned signature pattern and the delta
is stored in the Pattern Table.

@@

\textit{Lookahead Prefetching:} For each trigger to the prefetcher,
the first time that the SPP indexes into the PT, it does so in the
non-speculative manner.  We call it non-speculative because the
parameters which SPP uses to predict, like last block offset, incoming
block offset and signature are well-defined.  Assuming PT generates a
valid delta prediction (rather, up to 4 valid deltas), SPP enters into
the lookahead mode.

In the lookahead mode, SPP looks at the last generated delta(s),
chooses the one with the highest confidence and speculatively
generates the new effective address and the new signature.  Using
these new parameters, it re-accesses the PT to generate further
prefetches.  SPP keeps on repeating this cycle of accessing PT and
updating the signature based on highest confidence prefetch from the
last iteration.  These iteration count till which SPP manages to
predict prefetch entries in the lookahead manner is characterized as
its `depth'.  While doing this, SPP also keeps compounding the
confidence in each depth.  Thus as depth increases, overall confidence
keeps decreasing.  This makes sense since we are going deeper into the
speculation path.  When the confidence falls below a pre-defined
threshold, SPP stops further lookahead iterations.

\textbf{Global History Register:} One of the innovative ideas
introduced in SPP was the Global History Register, which bootstraps
learning across page boundaries.  GHR is a small 8-entry fully
associative structure.  Whenever a prefetch suggestion from the
Pattern Table crosses page boundaries, instead of completely
discarding it, GHR saves that information for inter-page learning.
Since the SPP-Perc implementation in this paper doesn't affect GHR
functionality in any ways, we won't be going into more details about
GHR.

\textbf{Prefetch Filter:} SPP also introduced the concept of Prefetch
Filter - a 1024 entry 1-way associative table which keeps a record of
last few entries prefetched by SPP.  This proves useful for following
reasons:
\begin{itemize}
\item \textbf{Eliminating duplicate prefetches}\newline Any subsequent
  prefetches recommended by SPP mechanism is checked against the
  existing entries in Prefetch Filter.  If a valid entry is found, it
  means that the particular cache line is already either in L2 Cache
  or being fetched.  Hence there is no need to issue a duplicate
  prefetch.

\item \textbf{Updating prefetcher}\newline If a subsequent demand
  access comes before eviction for a prefetch that was recommended by
  SPP, various components of SPP are updated to reflect that this was
  a good prefetch.  Correspondingly, if a prefetched cache line is
  evicted without being demand hit even once, SPP learns that this was
  a useless prefetch and updates the various tables accordingly

\item \textbf{Tracking Global Accuracy}\newline PF keeps a track of
  usefulness of the prefetches by introducing 2 counters:
  C\textsubscript{total} to track the total number of prefetches
  getting recorded in the PF and C\textsubscript{useful} to keep a
  track of which prefetches recorded in the PF led to a demand hit.
  The ratio C\textsubscript{useful} / C\textsubscript{total} is the
  global accuracy for the prefetching scheme.  It is represented as
  $\alpha$ in the paper.  The global accuracy acts a real-time
  throttler for the path confidence value as depicted in the following
  discussion.  \newline
\end{itemize}
\textbf{Confidence Tracking}: The PT keeps a track of hits to each
signature through a counter C\textsubscript{sig}.  The number of hits
for a given delta per signature are tracked using a counter
C\textsubscript{delta}.  The confidence for a given delta is
approximated through C\textsubscript{d} = C\textsubscript{delta} /
C\textsubscript{sig}.  When SPP enters into a lookahead mode, the path
confidence P\textsubscript{d} is given as:
$$P\textsubscript{d} \;=\; \alpha  \;.\;  C\textsubscript{d}  \;.\;  P\textsubscript{d-1}$$ where $\alpha$ is called the global accuracy and is calculated as shown in the Prefetch Filter section. 
The range of global accuracy is in [0,1].  The lower the value of
$\alpha$ for a given trace or a program phase, the overall confidence
is scaled down and this makes SPP less aggressive for the upcoming
prefetches.

Here d is the lookahead depth.  For d = 1, when SPP is in
non-speculative mode, P\textsubscript{0} can be thought of as 1.  Once
SPP enters into speculative mode, it calculates the path confidence as
a product of confidence of the individual prefetches encountered along
that path, further scaled using $\alpha$.  The final
P\textsubscript{d} is thresholded against prefetching-threshold
(T\textsubscript{p}) to decide whether to prefetch or not.  If yes,
then P\textsubscript{d} is thresholded against a numerically bigger
fill-threshold (T\textsubscript{f}) to decide whether the prefetch
should be sent to L2 Cache (high confidence prefetch) or Last Level
Cache (low confidence prefetch)

@@

\subsection{Case for an On-line Throttler}
As compared to some of the other state of the art prefetchers [BOP],
SPP is a far less aggressive prefetcher.  In the single core
environment, this gives BOP an edge as there is no resource contention
among the different cores.  Hence more aggressive prefetching is bound
to prove beneficial.  As we increase the core count, we observe that
SPP starts outperforming rest of the prefetchers.  This can be
attributed to the fact that each prefetch suggested by SPP is a
carefully calculated one and that prevents cache pollution.
\textit{<Figure showing the variation of SPP vs BOP wrt core count>}
For 4-core applications, SPP suggests XX\% fewer prefetches than BOP
and yet leads to higher IPC.

The above analysis shows that with a more careful throttling
mechanism, SPP can be tuned to become much more aggressive, leading to
increased coverage.  The onus of maintaining the accuracy now falls on
the independent throttler.  To test the hypothesis, we tuned down SPP
to the minimum possible threshold.  Only by doing this we managed to
increase the prefetch suggestions made by SPP, by XX\%.
\textit{<Comparison of SPP-Unleased with SPP / BOP>} Obviously this
came at a cost of increased DRAM traffic and cache pollution.

Moreover, the on-line confidence mechanism introduced in SPP was very
rudimentary.  It was based on taking a ratio C\textsubscript{d} =
C\textsubscript{delta} / C\textsubscript{sig} as explained above.  The
same confidence was used to make the decision whether to prefetch or
not to prefetch; and which level to prefetch.  While this
approximation was shown to work in the original SPP, we believe that a
better form of on-line decision making was possible.  Hence, it was
necessary to build a robust and adaptable learning mechanism to accept
/ reject the prefetch suggestions; and to decide the fill level (L2
Cache vs Last Level Cache).

>>>>

\section{Background Work and Motivation}
\label{Background}

@@

\subsection{Related Work}
\label{Background-Related}
The idea of prefetching has been around since Instruction Stream
Buffers were proposed by Jouppi~\cite{ISB}. Some of the earliest data
prefetchers developed to try to identify memory access patterns with a
constant stride pattern~\cite{Smith,Baer,Stride}. Major research was
dedicated to stride distance and depth prediction~\cite{Decoupled,Adaptive}. Newer prefetchers aimed at correlating
predictions with the past memory access addresses~\cite{Address_Correlated,AMPM}.

With time newer and more intricate prefetchers were
introduced~\cite{Wenisch_Temporal_Streaming,Stealth,Feedback_Directed,Coordinated,Bandwidth_Efficient,Pacman,TLB,Linearizing,Sandbox,VLDP,DoL,Domino}.
A whole class of streaming prefetchers developed on the lines of
Spatial / Temporal Memory
Streaming~\cite{Spatial_Pattern,SMS,Temporal_Instruction_Fetch,Off_Chip,STMS,SMS_JILP}.
There have been ideas for control flow speculation directed hardware prefetching~\cite{BFetch,MTBFetch}.

Most modern prefetchers aim at identifying complex memory access
patterns in a given application.  This allows them to capture some of
the irregular patterns seen in pointer chasing data-structures.
Offset based prefetchers are a generalization of the next-line
prefetcher.  Some of the prominent prefetchers exploiting this idea
are Sandbox Prefetcher~\cite{Sandbox} and the Best Offset Prefetcher~\cite{BOP}. 
Another class of prefetchers is lookahead Prefetchers.
Such prefetchers try to speculate deep into the application's memory
access trail.  These include Path Confidence based Lookahead
Prefetching~\cite{SPP} and Kill the Program Counter~\cite{KPC}.

@@

\textit{Machine Learning and Prefetching:} Peled \textit{et.al.}
introduce interesting ideas for on-line Reinforcement Learning and
dynamically scaling the magnitude of feedback given to the baseline
prefetcher~\cite{Semantics}. The biggest challenge here is that it
relies on compiler support for getting features to build the context.

The paper by Liao \textit{et. al.} focuses on prefetching for data
center applications~\cite{Datacenter}. They use offline Machine
Learning Algorithms like SVMs and Logistic Regressions to do
parametric search for an optimal prefetcher configuration.

%% NOTE: The below paper is literally the same idea as ours. But poor implementation and no good results. How much to bash this paper?
Finally, the paper on Data Cache Prefetching with Perceptron
Learning~\cite{BadPerc} talks about the idea of two step prefetching.
The first step is an existing baseline prefetcher while the second
step is a perceptron based throttler.  The paper has lots of
limitations in terms of design and implementation.  That reflects in
the fact that it did not lead to any significant performance gain over
even the basic prefetchers like the Stride Prefetcher~\cite{Stride} and
the Markov Prefetcher~\cite{Markov}.

\subsection{Perceptron Learning in Architecture}
\label{Background-Perceptron}
Perceptron learning for computer architecture design has been around
for a while.  It was first popularized by Jimenez \textit{et. al.} for
doing branch prediction~\cite{Perc_Branch}. In it's original
implementation, the Program Counter of the instruction looking for a
branch prediction would index into a given table of perceptron
weights.  The retrieved weights would then be multiplied with the
history of branch outcomes stored in the History Register (which is a
feature) in a dot product fashion.  The sum obtained is thresholded at
0 \textit{i.e.}, if the prediction y\textsubscript{out} >= 0, the
prediction is made as \textit{true}, or branch taken.  Else if the sum
is < 0, the prediction is made as \textit{false}.

The structure that we use is derived from the model introduced in
Piecewise Linear Branch Prediction~\cite{Piece_Linear}.  Here the
feature itself is used to index into a hash of perceptron weights.
This form of indexing makes sure that the hyper-plane learned by the
perceptron weights is able to differentiate between linearly
inseparable outcomes.  \textit{<Is it true? Not sure>}

Perceptron Learning for Reuse Prediction~\cite{Perc_Reuse} extended the
hash perceptron architecture to perform prediction in context of cache
replacement.  Perceptron layer can learn to correlate the cache
replacement behaviour with a variety of features.  Each feature has
its dedicated table of perceptron weights which it indexes into.
Hence number of tables equals the number of features.  Once the
perceptron weights from all the tables are obtained, they're summed
and thresholded based on a pre-decided value.  This led to a
prediction mechanism that is highly accurate, has quick learning rate
and is adaptable to changing program behaviour.  The features
introduced in that paper were derived from Program Counters of the
current and the last few instructions and from the memory address of the
current access.  Even with such basic features, high level of
correlation could be established by perceptrons.

The work was further extended by Multiperspective Reuse
Prediction~\cite{Multiperspective}, which introduced a varied set of
parametric features.  Although design space exploration for feature
and parameter selection was a non-trivial task, once fixed, it could
give a cache replacement predictor highly suitable for the given set
of applications.

@@

\textit{Perceptron Update Rule:} In all the above implementations, a
uniform perceptron update principle is being followed.  The weights
need to be updated if the prediction was wrong or the predicted sum
does not cross a certain threshold.  After a certain training period,
these weights are proportional to the probability of the outcome being
true.  This training threshold makes sure that the perceptrons are
trained till a certain level of confidence and yet they are not
over-trained to the given set.  Care is taken that the weights
saturate at certain positive and negative values so that they remain
confined to the bit-width.  The same rules will be applied in the
discussion done in Section \ref{Design-Perceptron} on NATCH learning algorithm.

\subsection{Prefetching with SPEC 2017}
\label{Background-SPEC2017}
\textit{<Discuss SPEC 2017 traces here>
<What are the possible graphs / analysis tools we can use for SPEC traces?>}

\subsection{Signature Path Prefetcher Architecture}
\label{Background-SPP}
Since the work we have done uses SPP~\cite{SPP} as the underlying prefetcher, we are
presenting a brief recap of the ideas introduced in the original
paper, especially with an eye towards their relevance in our work.
Signature Path Prefetcher (SPP) is a lookahead prefetcher and consists
of following structural components:

\textbf{Signature Table:} The ST keeps track of 256 most recently accessed
pages.  It is meant to capture memory access patterns within a page
boundary.  SPP indexes into an entry of ST using the page number.  For
each entry corresponding to a page, ST stores the `last block offset'
and `old signature'.  Last block offset is the block offset of the
last memory access of that given page.  The block offset is calculated
with respect to the page boundary.  The signature is a 12-bit
compressed representation of the past few memory accesses for that
page.  The signature is calculated as:
$$New Signature = (\,Old Signature << 3 bits\,) \;\;XOR\;\; (\,Delta\,)$$ 
In case a matching page entry is found, the stored signature in the corresponding entry is retrieved.

%% NOTE: Can we do away with this example? 
%%       If it looks like we are weiting too much about SPP
Consider the case that incoming page number 10 with a block offset 3
finds a match in the ST.  The retrieved pattern signature is 0x30 and
the Last Offset is 1.  Since now there is the Last Block Offset (1),
Incoming Block Offset (3), Old Signature (0x30), and New Signature
calculated as per above equation (0x182), SPP can infer
non-speculatively that the given pattern of memory accesses (as
captured in the Old Signature) leads to the particular Delta.  In
general, Delta is defined as the difference between the prefetch
suggestion block and the initial block which triggered the prefetch.
In this case, since SPP is in learning phase, it is defined as the
difference between the Incoming Block Offset and the Last Block Offset
(+2 in this case).  This, in turn generates the new memory pattern
(New Signature).  This newly learned signature pattern and the delta
is stored in the Pattern Table.

@@

\textit{Lookahead Prefetching:} On each trigger, SPP tries to go down
the program speculation path using its own prefetch suggestion.
Using current prefetch as the baseline, it re-accesses the PT to generate further
prefetches.  It keeps on repeating this cycle of accessing PT and
updating the signature based on highest confidence prefetch from the
last iteration.  These iteration count till which SPP manages to
predict prefetch entries in the lookahead manner is characterized as
its `depth'.  While doing this, SPP also keeps compounding the
confidence in each depth.  Thus as depth increases, overall confidence
keeps decreasing.

\textbf{Global History Register:} The GHR is a small 8-entry fully
associative structure to bootstrap learning across page boundaries. 
Whenever a prefetch suggestion from the
Pattern Table crosses page boundaries, instead of completely
discarding it, GHR saves that information for inter-page learning.
Since our NATCH implementation in this paper doesn't affect GHR
functionality in any ways, we won't be going into more details about
GHR.

\textbf{Prefetch Filter:} SPP also introduced the concept of Prefetch
Filter - a 1024 entry 1-way associative table which keeps a record of
last few entries prefetched.  This proves useful for following
reasons:
\begin{itemize}
\item \textbf{Eliminating duplicate prefetches}\newline Any subsequent
  prefetches recommended by SPP mechanism are checked against the
  existing entries in Prefetch Filter.  If a valid entry is found, it
  means that the particular cache line is already either in L2 Cache
  or being fetched.  Hence there is no need to issue a duplicate
  prefetch.

\item \textbf{Updating prefetcher}\newline Since the PF keeps a track
of past few prefetches, it uses that information to see if a given
prefetch led to a demand hit or a cache eviction. Using this information, 
SPP can update its internal states.

\item \textbf{Tracking Global Accuracy}\newline PF keeps a track of
  global usefulness ($\alpha$) of the prefetches by calculating 
  C\textsubscript{useful} / C\textsubscript{total}, where
  C\textsubscript{total} is the total number of prefetches
  getting recorded in the PF and C\textsubscript{useful} is the number 
  of prefetches that led to a demand hit.
\end{itemize}

\textbf{Confidence Tracking}: The PT keeps a track of hits to each
signature through a counter C\textsubscript{sig}.  The number of hits
for a given delta per signature are tracked using a counter
C\textsubscript{delta}.  The confidence for a given delta is
approximated through C\textsubscript{d} = C\textsubscript{delta} /
C\textsubscript{sig}.  When SPP enters into a lookahead mode, the path
confidence P\textsubscript{d} is given as:
$$P\textsubscript{d} \;=\; \alpha  \;.\;  C\textsubscript{d}  \;.\;  P\textsubscript{d-1}$$ where $\alpha$ is called the global accuracy and is calculated as shown previously. 
The range of global accuracy ($\alpha$) is [0,1].

Here d is the lookahead depth.  For d = 1, when SPP is in
non-speculative mode, P\textsubscript{0} can be thought of as 1. 
The final P\textsubscript{d} is thresholded against prefetching-threshold
(T\textsubscript{p}) to decide whether to prefetch or not.  If yes,
then P\textsubscript{d} is thresholded against a numerically bigger
fill-threshold (T\textsubscript{f}) to decide whether the prefetch
should be sent to L2 Cache (high confidence prefetch) or Last Level
Cache (low confidence prefetch)

@@

\subsection{Case for an On-line Throttler}
\label{Background-Case}
As compared to some of the other state of the art prefetchers [BOP],
SPP is a less aggressive prefetcher.  In the single core
environment, this gives BOP an edge as there is no resource contention
among the different cores.  Hence more aggressive prefetching is bound
to prove beneficial.  As we increase the core count, we observe that
SPP starts outperforming rest of the prefetchers.  This can be
attributed to the fact that each prefetch suggested by SPP is a
carefully calculated one and that prevents cache pollution.
\textit{<Figure showing the variation of SPP vs BOP wrt core count>}
For 4-core applications, SPP suggests XX\% fewer prefetches than BOP
and yet leads to higher IPC.

The above analysis shows that with a more careful throttling
mechanism, any prefetcher like SPP can be tuned to become much more aggressive, leading to
increased coverage.  The onus of maintaining the accuracy now falls on
the independent throttler.  To test the hypothesis, we tuned down SPP
to the minimum possible threshold.  Only by doing this we managed to
increase the prefetch suggestions made by SPP, by XX\%.
\textit{<Comparison of SPP-Unleased with SPP / BOP>} Obviously this
came at a cost of increased DRAM traffic and cache pollution.

Moreover, the on-line confidence mechanism introduced in SPP was very
rudimentary.  It was based on taking a ratio C\textsubscript{d} =
C\textsubscript{delta} / C\textsubscript{sig} as explained above.  The
same confidence was used to make the decision whether to prefetch or
not to prefetch; and which level to prefetch.  While this
approximation was shown to work in the original implementation, we believe that a
better form of generalised on-line decision making was possible.  
Hence, it was
necessary to build a robust and adaptable learning mechanism to accept
/ reject the prefetch suggestions; and to decide the fill level (L2
Cache vs Last Level Cache).
